Probing heavy ion collisions using quark and gluon jet substructure

### 2018-03-08 qg_ML.tex
YT updated the draft

The quenching mechanism in \textsc{Jewel} probed by telescoping deconstruction variables above can be further illuminated using the Lund diagram \cite{Andersson1989}. The Lund diagram~\cite{Andersson1989} is a diagrammatic jet representation associated with the Cambridge/Aachen clustering tree structure. It directly records the branching kinematics along the hard branches in the C/A clustering tree in terms of longitudinal momentum fraction $z$ of the soft branch and the angular separation $\Delta R$ between the two branches. The Lund diagram is then a two-dimensional histogram of variables $\ln (R/\Delta R)$ and $\ln z(\Delta R/R)$ where $R$ is the jet radius used in jet reconstruction. The variables are chosen such that the Lund diagram is uniform in the fixed strong coupling constant limit for jets in pp collisions due to the infrared structure of QCD and as such, they have been shown to be useful in distinguishing between QCD and boosted heavy particle jets \cite{Salam:2016yht}.

>>>>

The quenching mechanism in \textsc{Jewel} probed by telescoping deconstruction variables and soft-drop can be further illuminated using the Lund diagram \cite{Andersson1989}. The Lund diagram~\cite{Andersson1989} is a diagrammatic jet representation associated with the Cambridge/Aachen clustering tree structure. It directly records the branching kinematics along the hard branches in the C/A clustering tree in terms of longitudinal momentum fraction $z$ of the soft branch and the angular separation $\Delta R$ between the two branches. The Lund diagram is then a two-dimensional histogram of variables $\ln (R/\Delta R)$ and $\ln z(\Delta R/R)$ where $R$ is the jet radius used in jet reconstruction. The variables are chosen such that the Lund diagram is uniform in the fixed strong coupling constant limit for jets in pp collisions due to the infrared structure of QCD and as such, they have been shown to be useful in distinguishing between QCD and boosted heavy particle jets \cite{Salam:2016yht}.
